---
title: "Exam 3"
author: "Nathan Hernandez"
date: "Monday, December 08, 2014"
output: html_document
---

### Problem 1

1.a.  
```{r, echo=FALSE}
sheets <- rnorm(5, mean=0.1, sd=0.005)
plywood <- mean(sheets)
count = 10^4
sheets <- rnorm(count*5, mean=0.1, sd=0.005)
for(i in 1:count) {
    plywood[i] <- sheets[(i-1)*5+1]+sheets[(i-1)*5+2]+sheets[(i-1)*5+3]+sheets[(i-1)*5+4]+sheets[(i-1)*5+5]
}
summary(plywood)
```
  
1.b. This seems very reasonable to me.  
```{r, echo=FALSE}

h <- hist(plywood)
# curve(dnorm(x,mean=5,sd=0.005),4.95,5.05, add=TRUE, lwd=2, lty=5)
min <- plywood[which.min(plywood)]
max <- plywood[which.max(plywood)]
xfit<-seq(min,max,length=count) 
yfit<-dnorm(xfit,mean=mean(plywood,na.rm=TRUE),sd=sd(plywood,na.rm=TRUE)) 
yfit <- yfit*diff(h$mids[1:2])*length(plywood)
lines(xfit, yfit, col="blue", lwd=2, lty=5)
boxplot(plywood, horizontal=TRUE)
```

1.c. They are not meeting their goal. Only ~97% of boards fall within the range of 0.475 and 0.525 inches.
```{r,echo=FALSE}
mean <- mean(plywood)
sd <- sd(plywood)
(pnorm(0.525,mean,sd)-pnorm(0.475,mean,sd))*100
``` 

1.d. According to the Central Limit Theorem the sampling distribution of the mean should be ~0.1.
```{r,echo=FALSE}
#100 samples
sheets <- rnorm(100, mean=0.1, sd=0.005)
average <- mean(sheets)
average
```

### Problem 2

2.a.  
```{r, echo=FALSE}
FlightDelays <- read.csv(file = url("http://www1.appstate.edu/~thomleyje/data-files/FlightDelays.csv"))
library(boot)
boot.mean <- function(x,i){boot.mean <- mean(x$Delay[i])}

UA <- subset(FlightDelays, Carrier=="UA")
AA <- subset(FlightDelays, Carrier=="AA")

count <- 10^4


bootUA <- boot(UA, boot.mean, R = 10000)
bootAA <- boot(AA, boot.mean, R = 10000)

print(bootUA)
print(bootAA)


UAbca <- boot.ci(bootUA, type="bca")
AAbca <- boot.ci(bootAA, type="bca")


UAbca
AAbca


plot(bootUA)
plot(bootAA)
```

2.b.  
```{r,echo=FALSE}

FlightDelays <- read.csv(file = url("http://www1.appstate.edu/~thomleyje/data-files/FlightDelays.csv"))
library(boot)
boot.mean <- function(x,i){boot.mean <- mean(x$Delay[i])}

UA <- subset(FlightDelays, Carrier=="UA", select=Delay, drop=TRUE)
AA <- subset(FlightDelays, Carrier=="AA", select=Delay, drop=TRUE)

obs.stat <- mean(UA)/mean(AA)

count <- 10^4
my.bootavg <- numeric(count)
for(i in 1:count) {
  xua <- sample(UA,1123,replace=TRUE)
  xaa <- sample(AA,2906,replace=TRUE)
  my.bootavg[i] <- mean(xua)/mean(xaa)
}

hist(my.bootavg)
abline(v=c(obs.stat,mean(my.bootavg)),col=c("red","blue"))
boxplot(my.bootavg, horizontal=T)
mean(my.bootavg)
# sd(my.bootavg)

# bias <- mean(my.bootavg) - obs.stat   # computes estimated bias of the estimator
# bias                                
# rel.bias <- (bias/sd(my.bootavg))*100  # computes est. bias as a percentage of SE
# rel.bias
# 
# print(bootUA$t0/bootAA$t0)
# 
# hist(bootUA$t)
# hist(bootAA$t)

```


2.c. Yes, it is reasonable to assert that the mean delays for the two airliners are not the same.  
```{r, echo=FALSE}
print(confidence <- quantile(my.bootavg, c(.025, .975)))
```


2.d.  
```{r,echo=FALSE}
obs.stat <- mean(UA) / mean(AA)

bias <- mean(my.bootavg) - obs.stat

print(bias/sd(my.bootavg)*100)
```

2.e. This is almost certainly not true. Airliners have almost certainly optimized their process to reduce delay issues, but I'm sure at least occasionally one plane's stall will propagate through and stall other planes.













