---
title: "Exam 2"
author: "Nathan Hernandez"
date: "Monday, November 17, 2014"
output: html_document
---

### Problem 1
#### 1.a
```{r,echo=FALSE}
mm <- read.csv(file = url("http://www1.appstate.edu/~thomleyje/data-files/MandM.csv"))
marijuanaYes <- nrow(subset(mm, Marijuana=="Yes"))
marijuanaNo <- nrow(subset(mm, Marijuana=="No"))
marriageYes <- nrow(subset(mm, Marriage=="Yes"))
marriageNo <- nrow(subset(mm, Marriage=="No"))
matrix <- matrix(
  c(
    marijuanaYes,
    marijuanaNo,
    marriageYes,
    marriageNo
  ),
  ncol=2, 
  byrow=TRUE)
colnames(matrix) <- c("Yes","No")
rownames(matrix) <- c("Marijuana","Marriage")
table <- as.table(matrix)
table
```

#### 1.b
A test of homogeneity could be used to determine whether frequency counts are distributed identically across different populations.

#### 1.c
H~0~: P~states that allow marijuana use~ = P~states that allow same-sex marriage~  
H~1~: P~states that allow marijuana use~ ≠ P~states that allow same-sex marriage~

#### 1.d
```{r,echo=FALSE}
#selection <- subset(mm, select=Marijuana, drop=T)
#N <- 10^2
#result <- numeric(N)
# for(i in 1:N) {
#   index <- sample(50, size=6, replace=FALSE)
#   result[i] <- mean(selection[index]) - mean(selection[index])
# }
chisq.test(table(mm$Marijuana,mm$Marriage),correct=FALSE)
```
The null hypothesis can be rejected at 0.05.  

#### 1.e
The overall percentages of states that allow gay marriage and use of marijuana were dissimilar.

### Problem 2
#### 2.a
Region vs Marriage
```{r,echo=FALSE}
mm <- read.csv(file = url("http://www1.appstate.edu/~thomleyje/data-files/MandM.csv"))
tableMarriage <- table(mm$Region,mm$Marriage)
tableMarriage
```

Region vs Marijuana
```{r,echo=FALSE}
mm <- read.csv(file = url("http://www1.appstate.edu/~thomleyje/data-files/MandM.csv"))
tableMarijuana <- table(mm$Region,mm$Marijuana)
tableMarijuana
```

#### 2.b
A test of indepence could be used to determine whether there is an association between these two variables (same-sex marriage and marijuana acceptance).

#### 2.c
H~0~: Same-sex marriage and marijuana acceptance are independent.  
H~1~: Same-sex marriage and marijuana acceptance are not independent.

#### 2.d
```{r,echo=FALSE}
Midwest <- subset(mm, Region == "Midwest")
Midwest <- table(mm$Marriage,mm$Marriage)
chisq.test(Midwest, correct=FALSE)
South <- subset(mm, Region == "South")
South <- table(mm$Marriage,mm$Marriage)
chisq.test(South, correct=FALSE)
Pacific <- subset(mm, Region == "Pacific")
Pacific <- table(mm$Marriage,mm$Marriage)
chisq.test(Pacific, correct=FALSE)
West <- subset(mm, Region == "West")
West <- table(mm$Marriage,mm$Marriage)
chisq.test(West, correct=FALSE)
Northeast <- subset(mm, Region == "Northeast")
Northeast <- table(mm$Marriage,mm$Marriage)
chisq.test(Northeast, correct=FALSE)
```

#### 2.e



### Problem 3
N~0~: μ~First~ = μ~Second~  
N~1~: μ~First~ ≠ μ~Second~

```{r}
Draft <- read.csv(file = url("http://www1.appstate.edu/~thomleyje/data-files/Draft.csv"))
First <- subset(Draft, Half=="First")
Second <- subset(Draft, Half=="Second")
FirstMean <- mean(First$Number.1970)
SecondMean <- mean(Second$Number.1970)
obs.diff <- FirstMean - SecondMean
data <- subset(Draft, select=Number.1970, drop=T)
N <- 10^5-1
result <- numeric(N)
for(i in 1:N) {
  index <- sample(366, size=182, replace=FALSE)
  result[i] <- mean(data[index]) - mean(data[-index])
}
pvalue.upper <- (sum(result>=obs.diff)+1)/(N+1)
pvalue.lower <- (sum(result<=obs.diff)+1)/(N+1)
pvalue.two<-format(2*min(pvalue.upper,pvalue.lower),scientific=FALSE)
```
Obsereved difference of 45.45 and p-value of 0.00004. We can reject the null hypothesis.

### Problem 4
#### 4.a
One would expect to see 500/39 per number, or approximately 12.82051. This works out to 2.564% per number.  
Degrees of freedom: 38  
Expected frequency counts: 0.02564*500 = 12.82  

H~0~: The proportion of each number is equally represented.  
H~1~: The proportion of any number is not equally represented.

```{r,echo=FALSE}
lottery <- read.csv(file = url("http://www1.appstate.edu/~thomleyje/data-files/Lottery.csv"))
table <- table(lottery)
#prop.table(table)*100
table
chisq.test(table)
```
The null hypothesis cannot be rejected at 0.05.  

#### 4.b
One would expect to see 500/39 per number, or approximately 12.82051. This works out to 2.564% per number.  
Degrees of freedom: 38  
Expected frequency counts: 0.02564*500 = 12.82  

H~0~: The proportion of each number is equally represented.
H~1~: The proportion of any number is not equally represented.

```{r,echo=FALSE}
skulls <- read.csv(file = url("http://www1.appstate.edu/~thomleyje/data-files/EgyptianSkullsA.csv"))
table <- table(skulls)
chisq.test(skulls)
```
The null hypothesis cannot be rejected at 0.05.  



### Problem 5
H~0~ = The two variables are independent.  
H~1~ = The two variables are dependent.

The two variables are dependent between  the values of 3.8434 and 18.3834.  
```{r,echo=FALSE}
m<-3.8434
table <- matrix(c(m,10,10,m),ncol=2,byrow=TRUE)
colnames(table) <- c("B1","B2")
rownames(table) <- c("A1","A2")
table <- as.table(table)
chisq.test(table)

m<-18.3834
table <- matrix(c(m,10,10,m),ncol=2,byrow=TRUE)
colnames(table) <- c("B1","B2")
rownames(table) <- c("A1","A2")
table <- as.table(table)
chisq.test(table)
```
