---
title: "Homework 2"
author: "Nathan Hernandez"
date: "Sunday, September 21, 2014"
output: html_document
---

Part 1
============

**Problem 1**  
The set of data containing the elements {3, 5, 8, 15, 20, 21} produces a mean of 12 and a median of 11.5

```{r}
data <- c(3,5,8,15,20,21)
mean(data)
median(data)
```

If we apply the logarthim to our set of data an calculate the mean and median, we get 2.255966 and 2.393746 respectively. 

```{r}
logData <-log(data)
mean(logData)
median(logData)
```

Thus, we can conclude that neither mean nor median of our set of data is equivalent to the mean or median of our set of data after a logarithm function has been applied to the elements within the set of data.  

**Problem 2**  

This problem is functionally similar to problem 1, except that the data set and  function applied to the data set are different.

```{r}
data <- c(2,2,4,5,6,8,11,15)
mean(data)
median(data)
```

```{r}
sqrtData <-sqrt(data)
mean(sqrtData)
median(sqrtData)
```

**Problem 3**  

a. Only in the case where the real-valued function does not change the value of its input.

b. Only in the case where the real-valued function does not change the value of its input.

c. Yes, in the case where the real-valued function does not change the value of its input.

d. Yes, in the case where the real-valued function does not change the value of its input.

**Problem 4**  
a.
```{r}
FlightDelays <- read.csv(file = url("http://www1.appstate.edu/~thomleyje/data-files/FlightDelays.csv"))
DepartTime <- FlightDelays$DepartTime

table(DepartTime)
```

```{r, echo=FALSE}
barplot(prop.table(table(DepartTime))*100, xlab="Departure Times", ylab="Percentage")
```

b.
```{r}
prop.table(table(FlightDelays$Delayed30,FlightDelays$Day))*100
```

The percentage of flight delayed less than 30 minutes is:
```{r, echo=FALSE}
sum(prop.table(table(FlightDelays$Delayed30,FlightDelays$Day))[1,])*100
```

The percentage of flight delayed at least 30 minutes is:
```{r, echo=FALSE}
sum(prop.table(table(FlightDelays$Delayed30,FlightDelays$Day))[2,])*100
```

c.
```{r}
notDelayed <- subset(FlightDelays, Delayed30=='No')
delayed <- subset(FlightDelays, Delayed30=='Yes')
boxplot(notDelayed$FlightLength, delayed$FlightLength,
        names=c("Not Delayed", "Delayed"),
        col=c("green","red"),
        xlab="Flight Length",
        horizontal=TRUE)
```

d. It does appear that there is a relationship between the length of a flight and whether or not the departure is delayed at least 30 minutes. Longer flights seem to have a much higher chance of being delayed.

**Problem 5**  

a.
```{r}
Survey <- read.csv(file = url("http://www1.appstate.edu/~thomleyje/data-files/GSS2002.csv"))
DeathPenalty <- Survey$DeathPenalty
table(DeathPenalty)
```

```{r,echo=FALSE}
barplot(table(DeathPenalty), xlab="Responses", ylab="Response Count")
```

b. The summary command tells us how many people answered "NA," the table command does not.
```{r}
GunOwnership <- Survey$OwnGun
table(GunOwnership)
summary(GunOwnership)
```

c.
```{r}
prop.table(table(GunOwnership,DeathPenalty),1)*100
```

d. 80.46% of people who claimed they own a gun favor the death penalty. 65.33% of people who claimed they did not own a gun favored the death penalty. There does appear to be a difference of proportions in this regard. 


Part 2
============

**Problem 1**
```{r}
Berkeley <- read.csv(file = url("http://www1.appstate.edu/~thomleyje/data-files/Berkeley.csv"))
```

**Problem 2**
```{r}
Sex <- Berkeley$Sex
table(Sex)
```

```{r,echo=FALSE}
barplot(table(Sex), 
        col=c("pink","cyan"),
        xlab="Sex", 
        ylab="Number of Applicants")
```

**Problem 3**
```{r}
Department <- Berkeley$Department
table(Department)
```

```{r,echo=FALSE}
barplot(table(Department), 
        xlab="Department", 
        ylab="Number of Applicants")
```

**Problem 4**
```{r}
table(Sex,Department)
```

```{r,echo=FALSE}
barplot(table(Sex,Department), 
        col=c("pink","cyan"),
        main="Number of Applicants to Each Department by Gender",
        xlab="Department and Sex", 
        ylab="Number of Applicants")
```

**Problem 5**
```{r}
Status <- Berkeley$Status
round(prop.table(table(Status,Sex),2)*100,1)
```


**Problem 6**
```{r,echo=FALSE}
barplot(round(prop.table(table(Status,Sex),2)*100,1), 
        col=c("green","red"),
        main="Status by Gender",
        xlab="Gender", 
        ylab="Percentage of Accepted Applicants",
        beside=TRUE)
```

**Problem 7**
```{r}
DeptA <- subset(Berkeley, Department=='A')
DeptB <- subset(Berkeley, Department=='B')
DeptC <- subset(Berkeley, Department=='C')
DeptD <- subset(Berkeley, Department=='D')
DeptE <- subset(Berkeley, Department=='E')
DeptF <- subset(Berkeley, Department=='F')
```


**Problem 8**

a.
```{r}
round(prop.table(table(DeptA$Status,DeptA$Sex),2)*100,1)
```

```{r,echo=FALSE}
barplot(round(prop.table(table(DeptA$Status,DeptA$Sex),2)*100,1), 
        col=c("green","red"),
        main="Status by Gender",
        xlab="Gender", 
        ylab="Percentage of Accepted Applicants",
        beside=TRUE)
```

b.
```{r}
round(prop.table(table(DeptB$Status,DeptB$Sex),2)*100,1)
```

```{r,echo=FALSE}
barplot(round(prop.table(table(DeptB$Status,DeptB$Sex),2)*100,1), 
        col=c("green","red"),
        main="Status by Gender",
        xlab="Gender", 
        ylab="Percentage of Accepted Applicants",
        beside=TRUE)
```

c.
```{r}
round(prop.table(table(DeptC$Status,DeptC$Sex),2)*100,1)
```

```{r,echo=FALSE}
barplot(round(prop.table(table(DeptC$Status,DeptC$Sex),2)*100,1), 
        col=c("green","red"),
        main="Status by Gender",
        xlab="Gender", 
        ylab="Percentage of Accepted Applicants",
        beside=TRUE)
```

d.
```{r}
round(prop.table(table(DeptD$Status,DeptD$Sex),2)*100,1)
```

```{r,echo=FALSE}
barplot(round(prop.table(table(DeptD$Status,DeptD$Sex),2)*100,1), 
        col=c("green","red"),
        main="Status by Gender",
        xlab="Gender", 
        ylab="Percentage of Accepted Applicants",
        beside=TRUE)
```

e.
```{r}
round(prop.table(table(DeptE$Status,DeptE$Sex),2)*100,1)
```

```{r,echo=FALSE}
barplot(round(prop.table(table(DeptE$Status,DeptE$Sex),2)*100,1), 
        col=c("green","red"),
        main="Status by Gender",
        xlab="Gender", 
        ylab="Percentage of Accepted Applicants",
        beside=TRUE)
```

f.
```{r}
round(prop.table(table(DeptF$Status,DeptF$Sex),2)*100,1)
```

```{r,echo=FALSE}
barplot(round(prop.table(table(DeptF$Status,DeptF$Sex),2)*100,1), 
        col=c("green","red"),
        main="Status by Gender",
        xlab="Gender", 
        ylab="Percentage of Accepted Applicants",
        beside=TRUE)
```
