---
title: "Homework 2"
author: "Nathan Hernandez"
date: "Sunday, September 21, 2014"
output: html_document
---

**Problem 1**  
The set of data containing the elements {3, 5, 8, 15, 20, 21} produces a mean of 12 and a median of 11.5

```{r}
data <- c(3,5,8,15,20,21)
mean(data)
median(data)
```

If we apply the logarthim to our set of data an calculate the mean and median, we get 2.255966 and 2.393746 respectively. 

```{r}
logData <-log(data)
mean(logData)
median(logData)
```

Thus, we can conclude that neither mean nor median of our set of data is equivalent to the mean or median of our set of data after a logarithm function has been applied to the elements within the set of data.  

**Problem 2**  

This problem is functionally similar to problem 1, except that the data set and  function applied to the data set are different.

```{r}
data <- c(2,2,4,5,6,8,11,15)
mean(data)
median(data)
```

```{r}
sqrtData <-sqrt(data)
mean(sqrtData)
median(sqrtData)
```

**Problem 3**  

a. Only in the case where the real-valued function does not change the value of its input.

b. Only in the case where the real-valued function does not change the value of its input.

c. Yes, in the case where the real-valued function does not change the value of its input.

d. Yes, in the case where the real-valued function does not change the value of its input.

**Problem 4**  
a.
```{r}
FlightDelays <- read.csv(file = url("http://www1.appstate.edu/~thomleyje/data-files/FlightDelays.csv"))
DepartTime <- FlightDelays$DepartTime

table(DepartTime)
```

```{r, echo=FALSE}
barplot(prop.table(table(DepartTime))*100, xlab="Departure Times", ylab="Percentage")
```

b.
```{r}
prop.table(table(FlightDelays$Delayed30,FlightDelays$Day))*100
```

The percentage of flight delayed less than 30 minutes is:
```{r, echo=FALSE}
sum(prop.table(table(FlightDelays$Delayed30,FlightDelays$Day))[1,])*100
```

The percentage of flight delayed at least 30 minutes is:
```{r, echo=FALSE}
sum(prop.table(table(FlightDelays$Delayed30,FlightDelays$Day))[2,])*100
```

c.
